%!TEX root = ../../../super_main.tex

\section{Missing Applications in Grid}
\label{sec:missing_apps_racecondition}

We revealed an issue in the application grid, specifically with the background tasks that load the applications and their icons. The application grid in the \launcher's \androidinline{HomeActivity} would sometimes not show the applications. This issue occurs when the \launcher is loading its applications upon startup. The \launcher starts a background task in its \androidinline{onResume} method which loads and prepares the applications to be shown.
\\\\
This bug occurs when the \androidinline{onResume} method of the \androidinline{HomeActivity} checks a boolean variable called \androidinline{mIsAppsContainerInitialized}, which was used in the previous solution to populate the application grid (see \secref{sec:reengineering_of_application_grid}). The previous solution included rebuilding a complicated layout called \androidinline{AppsContainer}, based on \androidinline{LinearLayout} objects, every time the grid had to change. This layout was built on a background thread in a \androidinline{LoadHomeActivityApplicationTask}. Once the layout was completed on the background thread, the variable \androidinline{mIsAppsContainerInitialized} was set to true. A check on the variable was then performed to verify whether or not the application screen should be reloaded.

The check on \androidinline{mIsAppsContainerInitialized} still happened after we implemented the changes described in \secref{sec:reengineering_of_application_grid}, as it did not seem to have any effect in most cases. Since it has been discovered that errors sometimes happen because of this check, and we no longer have any need to verify that we are done building any layouts, the piece of code has been removed.