%!TEX root = ../../../super_main.tex
\section{Wrong User Permissions}
\label{sec:wrong_user_permissions}

In the \giraf-applications, there exists three types of profiles, namely \emph{Administrator}, \emph{Guardian}, and \emph{Citizen}. Administrators have the most permissions in the system, and are allowed to do anything a guardian can do, as well as create guardian profiles and citizen profiles. Guardians manage some set of citizens, for instance the citizens connected to a specific institution, or a subset of an institution. Guardians can use the different applications, and the configure the settings and applications for citizens they manage. Citizens are allowed to use different applications, namely the ones that have been added to their profile by one of their guardians. 
\\\\
However, these different profile-types are not enforced correctly in the \launcher application. Currently, guardian and citizen profiles have access to the same features. For instance, a citizen may access the settings-panel and choose which applications that should be accessible for that same citizen. This feature should only be available for guardian and administrator profiles.
\\\\
Before a guardian hands the tablet to a citizen, the guardian needs to switch profile to that specific citizen, so that the system knows what features should be available. Only guardians or administrators should be allowed to switch profiles. Currently all profile types are able to switch profiles, meaning that citizens themselves can switch to a guardian profile and thereby gain access to parts of the application that should otherwise be unavailable for them.
\\\\
We fixed the problem by checking the type of the active profile. The buttons which allowed for switching profiles and settings would then be hidden if the current user is not a guardian or administrator.