%!TEX root = ../../super_main.tex
\part{First Sprint}
\label{par:first_sprint}

\chapter{Sprint Overview}
The focus of the first sprint, for all project groups across the multi-project, was to stabilize and get an overview of the project. The project was inherited from former $6^{th}$ semester project groups, and not many of the current $6^{th}$ semester students knew what the \giraf project was about.
\\\\
Getting started with the project included setting up development tools and environments e.g. Android Studio (Integrated Development Environment), Git (Version control), and, Jenkins (Continuous Integration Server). It also included getting the code base to a more stable and useful state, from the user's perspective. Per request of the customers, this new state of the system should ideally not include any new features.
\\\\
\todo{DONE-start}In the beginning of the first sprint, a Scrum Planning Meeting was held. During this meeting the customers was not present at this meeting, however the developers of \giraf had spent some time reading the reports from previous semesters and fetching the requirements and priorities set by the customers last year. \tabref{tab:application_priorities_sprint_one} shows how the different applications were prioritized by the customers, with 0 being the highest priority. Please note that these different priorities do not reflect which applications the customers wants us to focus on, but rather which applications are important for them. So for instance, if an application has a high priority, but is almost ``done'' then it would require less man hours. The prioritization is not a scale of how much time should be spent on a given application but a scale of how important an application i to become stable, meaning that an application with a high priority might be so stable that no work is required. \todo{DONE-end}


\begin{table}[!htbp]
	\center
    \begin{tabular}{l l}
        \textbf{Application}     & \textbf{Priority} \\ \hline\hline
        \launcher                & 0                 \\ \hline
        \gc         		     & 1                 \\ \hline
        \emph{Picto Search}      & 2                 \\ \hline
        \emph{Week Schedule}     & 3                 \\ \hline
        \emph{Sequence}          & 4                 \\ \hline
        \emph{Picto Reader}      & 5                 \\ \hline
        \emph{Picto Creator}     & 6                 \\ \hline
        \ct                      & 8                 \\ \hline
        \emph{Profile Manager}   & 7                 \\ \hline
        \emph{Timer}             & 9                 \\ \hline
        \emph{Voice Game}        & 10                \\ \hline
        \emph{Category Game}     & 11                \\ \hline
        \emph{Life Story}        & 12                \\ \hline
        \emph{Web admin}         & 13                \\ \hline
    \end{tabular}
    \caption{Application priorities}
    \label{tab:application_priorities_sprint_one}
\end{table}

\FloatBarrier

Our group opted for, and got assigned to, the task improving the \giraf-\launcher application during a meeting between representatives of the GUI project area groups.

\input{content/sprint_1/launcher}

\input{content/sprint_1/android_guidelines}

\input{content/sprint_1/issues_solutions/issues_solutions}

\input{content/sprint_1/conclusion}
