%!TEX root = ../../super_main.tex
\chapter{Introduction}
\label{cha:introduction}

%Technology can enhance the quality of our lives in many different ways. A new airbag technology in our cars or an intelligent thermostat in our house. New technology helps us on many different aspects. These technologies also includes software, that enables devices to assist people in new and innovative ways.
%\\\\
% Purpose of software
This report focuses on the continued development of an existing \emph{Android}-software suite for tablets called \giraf (Graphical Interface Resources for Autistic Folk), which includes tools and games to assist and train everyday aspects of life for citizens diagnosed an Autism Spectrum Disorder (ASD) \parencite{asd}. The tool is currently in development but should, when finished, be used as an digital alternative to the already existing tools and techniques used \parencite{birken_slides}.
\\\\ 
This system has three types of users, the citizens diagnosed with ASD and the institutional or legal guardians of these citizens. Using \giraf, a citizen can find tools to mimic and learn social patterns. This tool is also an alternative to communication for citizens since many people diagnosed with ASD have weak or none verbal language. The guardians customize the various application such that they are optimized for the needs of the individual citizens. The last type of users is the administrators who are allowed to manipulate with users and profiles in the system. This roles may not use the tools, but rather ensure that the citizens and guardians can use it, and that their devices are correctly configured.
\\\\
The primary customer of \giraf is the municipality of Aalborg, where one of the main stakeholders of the \giraf-system is a kindergarten called \emph{Birken}. This kindergarten takes care of children diagnosed with ASD. The staff in \emph{Birken} spend a lot of time preparing physical and visual weekly schedules and checklists based on laminated printouts for the children which helps with their daily functions. This has motivated some of the previous developers of the \giraf project to try to digitize the schedule and checklists currently used \parencite{birken_slides}.

\input{content/introduction/multi_project_organisation}

