%!TEX root = ../../super_main.tex
\part{Third Sprint}
\label{par:third_sprint}

\chapter{Sprint Overview}
In the third sprint, our group handed over the task of creating and maintaining the shared GUI components of the project (commonly referred to as \gc) to another group. This transfer of responsibility has been done in order for our group to finish the \ct before the start of the fourth sprint. The workload of both the \ct and the \gc was too much for our group to guarantee that we could complete both tasks. The focus of this sprint is therefore to finish up the \ct and ensure that it is stable after this sprint.
\\\\
At the start of the third sprint, the \ct was in a state where guardians were able to create categories and view their content. It was not possible to add pictograms to a category. It was possible to view and modify categories for both the institution and individual citizens.
\\\\
What is currently missing is the feature that opens \ps and allows a user to search for specific pictograms and adding them to a desired category. Furthermore, the concept of transferring guardian/institution categories onto citizen profiles and being able to modify individual citizen categories without affecting any of the others. Another missing feature is the possibility of editing a guardian/institution category and then cascading any changes down onto every citizen category which is a child of this super-category. In addition, some memory issues have been discovered when a list of pictograms in a category becomes too large which has to be solved. 
\\\\
At the Sprint Planning Meeting, the applications were once again prioritized by the customers. \tabref{tab:application_priorities_sprint_three} shows how the customers have prioritized the different applications for the third sprint.

\begin{table}[!htbp]
	\center
    \begin{tabular}{l l}
        \textbf{Application}     & \textbf{Priority} \\ \hline\hline
        \launcher                & 0                 \\ \hline
        \gc         		     & 0                 \\ \hline
        \emph{Picto Creator}     & 1                 \\ \hline
        \ct                      & 2                 \\ \hline
        \emph{Sequence}          & 3                 \\ \hline
        \emph{Week Schedule}     & 4                 \\ \hline
        \emph{Profile Manager}   & 5                \\ \hline
        \emph{Picto Search}      & 6                 \\ \hline
        \emph{Picto Reader}      & 7                 \\ \hline
        \emph{Timer}             & 8                 \\ \hline
        \emph{Life Story}        & 8                 \\ \hline
        \emph{Category Game}     & 8                 \\ \hline
        \emph{Voice Game}        & 8                 \\ \hline
        \emph{Web admin}         & 8                 \\ \hline
    \end{tabular}
    \caption{Application priorities}
    \label{tab:application_priorities_sprint_three}
\end{table}

\FloatBarrier

\input{content/sprint_3/issues_solutions/issues_solutions}

\input{content/sprint_3/collaboration/collaboration}

\input{content/sprint_3/conclusion}