%!TEX root = ../../../super_main.tex

\chapter{Design Manual}
\label{cha:design_manual}

Throughout the fourth sprint, development of the design manual had a high priority for our group. Roughly half of the group's resources were used on the development of the manual. From the start, we knew that we would not be able to complete the design manual. This was partly because we estimated it to be too much work, and also because we knew that there were still open design problems that needed attention. Our focus was therefore to get already agreed-upon design guidelines formalized. The reasoning behind the development of the design manual, and the use of it is described in this chapter. The latest version of the design manual can be found in \appref{app:design_manual}.

\section{Development}
\label{sec:development}
In the third sprint, a GUI design-meeting was arranged to ensure that new and previous GUI-groups all agreed on the same design principles.  The results of this meeting were meant to be implemented in the former design guidelines made by group \emph{SW606F15}. However, this was only documented on a note basis, and would not be instructive to new \giraf developers about the design. Because of this, it was prioritized to get these notes formalized and described in details in the new design manual. The previous design guide can, as previously mentioned, be found in their report\footnote{This report has not yet been published, and we are therefore unable to cite it properly}.

\section{Complying with the Manual}
\label{sec:complying_with_the_manual}
While developing the manual, we looked at the different applications in the \giraf software suite to see if we could help other groups with improving the design of their applications so that their applications could become more usable and more consistent with the other applications. After checking the different applications, we sat down with members from the various groups and gave them a walk-through of the issues we found, such that they had time to correct the issues or document them properly before the Sprint Review Meeting.
\\\\
While looking through the different applications, we found some design cases that were not considered in the developed design manual. Due to limited time in the fourth sprint, it was decided not to write additional sections in the manual to cover these cases. Instead of just deciding upon the design in these cases for ourself, we have written notes throughout the design-manual to indicate where the design is incomplete or needs attention. These notes describe the different choices that the next generation of \giraf developers will have to consider in order to complete the manual. Ideally, the groups next semester should have a meeting between all GUI-groups to discuss how design issues should be resolved.