%!TEX root = ../../super_main.tex
\part{Second Sprint}
\label{par:second_sprint}

\chapter{Sprint Overview}
\label{sec:sprint2_overview}
The focus of the second sprint was to complete and stabilize the applications with the highest assigned priority, the priorities are listed in \tabref{tab:application_priorities_sprint_two}, which was determined with the customers. The costumers were asked to prioritize the list of existing applications, with 0 being the highest priority, during the Sprint Planning Meeting for the second sprint. Application responsibilities were then divided among the GUI-groups. Some applications do not have a priority because the customers could not relate to these.

\todo{Write intro what will be described in this chapter.}

\begin{table}[!htbp]
	\center
    \begin{tabular}{l l}
        \textbf{Application}     & \textbf{Priority} \\ \hline\hline
        \launcher                & 0                 \\ \hline
        \emph{Picto Search}      & 1                 \\ \hline
        \emph{Week Schedule}     & 2                 \\ \hline
        \emph{Sequence}          & 3                 \\ \hline
        \emph{Picto Creator}     & 4                 \\ \hline
        \ct                      & 5                 \\ \hline
        \emph{Picto Reader}      & 6                 \\ \hline
        \emph{Timer}             & 6.5               \\ \hline
        \emph{Life Story}        & 7                 \\ \hline
        \emph{Category Game}     & 8                 \\ \hline
        \emph{Voice Game}        & 9                 \\ \hline
        \emph{Profile Manager}   & 10                \\ \hline
        \emph{Web admin}         & -                 \\ \hline
        \gc         		     & -                 \\ \hline
    \end{tabular}
    \caption{Application priorities}
    \label{tab:application_priorities_sprint_two}
\end{table}

\FloatBarrier

We did not really have any project preferences for this sprint, since we already brought the \launcher to a stable state. The \giraf \ct was given a high priority at the Sprint Planning Meeting for the second sprint, and we got assigned to this project since we did not have any preferences. 

\section{Category Tool and Components}
\label{sec:category_tool_and_components}

The \giraf \ct is an application which is used by guardians to create and manage pictogram categories. These categories are used across many different applications, for instance the \emph{Category Game} application also known as \emph{Train}.
\\\\
We were also assigned to construct a series of standard components for the \gc library. These standard components should, as of the start of the second sprint, include: A specialization of the Android \androidinline{ActionBar} for \giraf, buttons with automatically scaling text, and a standard dialog to use across all applications.

\input{content/sprint_2/initial_thoughts}

\input{content/sprint_2/issues_solutions/issues_solutions}

\input{content/sprint_2/conclusion}