%!TEX root = ../../super_main.tex
\chapter{Semester Conclusion}
\label{cha:conclusion_final}

The reader is invited to reference \appref{app:screenshots_of_the_finished_applications}, containing screenshots of the final version of the developed applications and components, while reading this chapter. The applications can also be downloaded from the Google Play store \parencite{giraf_google_play}.

\section*{\launcher}
The \launcher is the main entry point to the \giraf system, and our group have been responsible for maintaining and further developing the application throughout the semester. The \launcher was found to be unstable in the early development. After four sprints of development, our group have brought significant improvements to the \launcher, in terms of both stability and usability.
\\\\
The overall stability of the \launcher has been improved, which for instance has been achieved by properly utilizing Android fragments in the \launcher settings, and making sure that the GUI thread is kept free from heavy processing. 
\\\\
The usability has been improved by streamlining the design, and by optimizing features such as the newly implemented view pager in the home screen of the \launcher.

\section*{\emph{Category Tool}}
The \ct was not able to compile when it was assigned to our group. When the \ct was brought to a running state, it was found that the design was highly inconsistent and did not follow basic design principles. The application was in such a bad condition, that a redesign was found to be the best approach in contrast to repairing it.
\\\\
Avoiding the pitfalls that made the old design horrible, along with following the Android guidelines, had a high priority in the redesign of the \ct. This included splitting the functionality of the tool into logically grouped screens, for instance splitting the action of viewing categories and creating categories into two different activities.
\\\\
We did not want to add unused features from the previous version in the new design, such as coloring categories. Therefore, during the redesign, the relevant user stories for the \ct were found. These user stories included, but were not limited to, general management of categories, e.g. creating and removing categories as well as populating categories with pictograms. These user stories were then implemented and unused features were avoided. 
\\\\
Furthermore, we were given new user stories for the \ct, such as templates of categories that can be copied to citizens and then later customized further. The found user stories were all implemented and satisfied the customers. Usability evaluation indicated that the \ct worked as intended with only a few cosmetic problems.

\section*{\giraf \emph{Components} and Design Manual}
In the early stage of the development, a lot of new components were introduced to the \gc library in order to streamline the design of the \giraf applications. However, since we got the responsibility for implementing these shared components, it motivated us to create a knowledge base for the development, such that our work and choices regarding design would not be lost for the next $6^{th}$ semester students. 
\\\\
One of the main reasons that we wanted to make a proper documentation is the fact that, when we started developing there was no central knowledge base assisting us on how we should approach the development. This meant that we had no reasons as to why any of the previous \giraf developers had made the design as they did. Therefore, when creating the design manual and the shared components, we wanted them to work nicely together such that it would be easier to maintain and further develop in the future. For this reason, we think that this might be our most significant contribution to the overall project.